---
title: "CyberThreats"
author: "Tyler Brown"
date: "`r Sys.Date()`"
output: html_document
---
## Import Libraries
```{r}
library(tidyr)
library(dplyr)
```

## Read the Data
```{r}
url = 'https://raw.githubusercontent.com/AlphaCurse/CyberThreats/main/cyberthreats.csv'
df = read.csv(url)
head(df)
```

## Tidy and Transform Data
```{r}
colnames(df)[1] = 'Year'

df = df[order(-df$Year),]
df$Adware = as.integer(gsub(",","",df$Adware))
df$Ransomware = as.integer(gsub(",","",df$Ransomware))
head(df)
```

## Analysis comparing the most cyber threats over 2017 to 2022

```{r}
df$Total = rowSums(df[ , c(2, 3, 4, 5)], na.rm = TRUE)
head(df)
```
Below, I have calculated the probability of cyber threats occurring from 2017 to 2022. As we can see, 2017 has a 12.42% probability, 2018 has a 11.14% probability, 2019 has a 18.77% probability, 2020 has a 22.98% probability, 2021 has a 13.25% probability, and 2022 has a 21.45% probability. Due to COVID-19 in 2018, 2019 and 2020, we can see an increase in cyber threats that quickly drops in 2021. Seeing as many employers kept their employees working remotely, the probability of receiving a cyber attack is higher than when employees were inhouse.

```{r}
year_2022 = (5630/(5630+3477+6032+4927+2924+3260))*100
year_2021 = (3477/(5630+3477+6032+4927+2924+3260))*100
year_2020 = (6032/(5630+3477+6032+4927+2924+3260))*100
year_2019 = (4927/(5630+3477+6032+4927+2924+3260))*100
year_2018 = (2924/(5630+3477+6032+4927+2924+3260))*100
year_2017 = (3260/(5630+3477+6032+4927+2924+3260))*100

year_2022
year_2021
year_2020
year_2019
year_2018
year_2017
```